Results

### 2024-04-12 manuscript.Rmd
- Rendered website
deleting large files

abstract          : "Privacy is defined as a voluntary withdrawal from society. While everyone needs some degree of privacy, we currently know little about who needs how much. In this study, we explored the relations between the need for privacy and personality. Personality was operationalized using the HEXACO personality inventory. Need for privacy was measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy). A sample of 1,576 respondents representative of the U.S. in terms of age, gender, and ethnicity was collected. The results showed several substantial relationships: More extraverted people needed substantially more privacy. People less honest, less fair, and less altruistic needed more privacy, lending some support to the nothing to hide-argument. More conservative respondents needed more privacy from the government."
keywords          : "Privacy, need for privacy, personality, HEXACO"

@@

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
library(devtools)
library(english)
library(ggplot2)
library(kableExtra)
library(lavaan)
library(magrittr)
library(naniar)
library(papaja)
library(semPlot)
library(simsem)
library(td)
library(tidyverse)

load("data/workspace_2.RData")

@@

<!-- The increasing digitization of everyday life has catapulted  -->
<!-- which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016],  -->
Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2023].
Yet despite its importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155].
<!-- Why do some people desire more and some people desire less privacy? -->
What can we infer about a person if they desire more privacy?
Are they more introverted, more risk-averse, or more traditional?
<!-- Or do they have more to hide? -->
Asking these questions seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007], which is that people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear. 
Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
Or are people simply less extraverted, more diligent, or more prudent? 
With this paper, we seek to answer the following question: 
What can we learn about a person’s personality if they say they desire more privacy?

<!-- This study therefore seeks to understand how the need for privacy is related to dimensions and facets of personality. -->

<!-- It states that data mining and surveillance by government entities poses no threat to the privacy of law-abiding citizens, and is only problematic for people who are engaged in illegal activities who want to hide their information [@soloveVeGotNothing2007, p. 753]. -->
<!-- Summarized as “If you have nothing to hide, you have nothing to fear”, it implies that people who desire more privacy are also more likely to be involved in incriminating activities.  -->
<!-- It is true that people who commit crimes and who are insincere would indeed benefit from greater privacy.  -->
<!-- However, there exist many alternative reasons as to why people feel a greater or lesser need for privacy.  -->
<!-- Among those reasons are dispositional explanations.  -->
<!-- For example, people who need more privacy may be simply more introverted, hesitant, or prudent.  -->

<!-- A better understanding of the relation between personality and privacy is thus useful to illuminate the full range of human motivation for desiring privacy, and thus understanding individual decision-making and behavior surrounding personal privacy.  -->
<!-- Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155].  -->
<!-- However, to date there is almost no empirical research that can be used to develop well-informed hypotheses.  -->

@@

<!-- We first outline our own understanding of privacy, because the theoretical concept of privacy is multidisciplinary, complicated, and contested [@nissenbaumPrivacyContextTechnology2010, p. 71].  -->
Privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
This withdrawal happens _voluntarily_, and it is under a person's _control_ [@westinPrivacyFreedom1967]. 
Privacy is also multi-dimensional. 
On the broadest level, we can differentiate the two dimensions of horizontal and vertical privacy [@schwartzSocialPsychologyPrivacy1968; @masurPrivatheitOnlineKommunikation2018].
Whereas horizontal privacy captures withdrawal from other people or peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or businesses). 
In her theoretical analysis, @burgoonPrivacyCommunication1982 argued that privacy has four more specific dimensions: informational, social, psychological, and physical privacy. 
@pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
reserve ("unwillingness to be with and talk with others, especially strangers," p. 1293); isolation ("desire to be alone and away from others," p. 1293), solitude ("being alone by oneself and free from observation by others," p. 1293), intimacy with friends ("being alone with friends," p. 1293), intimacy with family ("being alone with members of one's own family," p. 1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention," p. 1293). 
<!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].  -->
<!-- Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people _think_ can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) [@dienlinPrivacyProcessModel2014]. -->
Building on these understandings of privacy, in this study we employ a multifaceted model of need for privacy. 
We focus on _vertical_ privacy with regard to people’s felt need for withdrawal from surveillance by a) the government and b) private companies; 
_horizontal_ privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
and _general_ privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
Although all of these dimensions were defined and established in prior research, combining these dimensions into one single comprehensive measure of privacy represents a novel approach.

Acknowledging that various understandings of personality exist, we operationalize personality using the factors and facets of the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018]. 
HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant aspects than other operationalizations. 
The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
<!-- and represents a broad understanding of personality-->
It includes six factors (discussed below), which have four specific facets each. 
In addition, the HEXACO model includes a sixth factor not present in the Big Five labeled honesty-humility (plus a meta-facet called altruism), which seem particularly well-suited to investigate the nothing-to-hide-argument.

@@

So far, only few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
Moreover, we are not aware of a viable theory specifically connecting privacy and personality.
Due to the dearth of empirical studies and the lack of theory, in this study we hence adopt an exploratory perspective. 
<!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->

In order to understand how personality might relate to privacy, we can ask the following question: 
Why do people desire privacy?
Privacy is important.
But according to @trepteNeedPrivacy2017, the need for privacy is only a secondary need---not an end in itself.
Accordingly, privacy satisfies other more fundamental needs such as safety, sexuality, recovery, or contemplation.
@westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships). 
Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and thereby social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
But privacy can also have negative aspects. 
It is possible to have too much privacy.
Being cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
<!-- The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information [@petronioCommunicationPrivacyManagement2010].  -->
And privacy can also help conceal wrongdoing or crime.

<!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].
Confronted with a threat---for example, the prototypical tiger---people are inclined to withdraw.
In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities. 
Indeed, the need for privacy may have evolved precisely because it offers such advantages.

@@

Empirical studies have linked privacy to increased cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
@coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
In the surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
In the privacy condition, the experimenter could not see the students. 
Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
<!-- While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty. -->
In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28). 
<!-- Together, these studies suggest the possibility that lack of honesty may relate to an increased need for privacy, especially when it comes to government surveillance.    -->

We do not mean to suggest that it is only dishonest people who feel a need for privacy.
Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].
A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].
Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.
Considering all the evidence, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies. 
<!-- , as governments have the legitimate power to prosecute illegal activities.  -->
<!-- Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.  -->
<!-- Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities. -->

@@

<!-- Need for privacy might relate to a person’s level of emotionality.  -->
Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
Anxious people might hence desire more privacy. 
People who are more concerned about their privacy (in other words, more anxious about privacy) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
On the other hand, the opposite may also be true: 
People who are more anxious in general may desire less privacy from others (especially their strong ties), as a means to cope better with their daily challenges or to seek social approval to either verify or dispel their social anxiety.

@@

Comprising the facets social self-esteem, social boldness, sociability, and liveliness, extraversion is arguably the factor that should correspond most closely to need for privacy. 
<!-- This especially pertains to the sociability facet, which captures whether people prefer to spend their time alone or with company.  -->
<!-- It is plausible that  -->
Conceptually, social privacy and sociability are closely related.
More sociable people are likely more inclined to think of other people as a resource, and thus they should desire less horizontal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001]. 
Given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.

@@

Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
Arguably, all facets are about being in control, about reducing relevant risks and future costs.
Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully might prefer to have more privacy because it affords them greater control. 
Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for vertical privacy. 
In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018]. 
Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
<!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.  -->
<!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->

@@

### Socio-demographic variables

The need for privacy should also be related to sociodemographic aspects, such as sex, age, education, and income. 
For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2023].
In a nationally representative study of the U.S. and Japan, people who were older and who had higher income reported more privacy concern. 
More educated people possess more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and as a consequence they might desire more privacy. 
Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, although not necessarily from other people. 
Some minorities groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
Last, we will examine whether one’s political position is related to the need for privacy. 
We could imagine that more right-leaning people desire more privacy from the government, but not necessarily from other people.
People who are more conservative tend to trust the government slightly less [@cookSkepticalAmericanRevisiting2005], which might be associated with an increased need for privacy.
We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy.

@@

This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
The Study was conducted as an online questionnaire, programmed with Qualtrics.
The survey can be found in the [online supplementary material](https://osf.io/e47yw/files/osfstorage/65c363e69b32ca0b4397f002).

@@

To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
We based our power analysis on a smallest effect size of interest (SESOI; see below).
We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. <!-- Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain.  -->
<!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
To estimate power, we simulated data.
We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10 (the SESOI).
We, furthermore, set the latent factor loadings to be $\lambda$ = .85.
<!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
<!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.
A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
To account for potential attrition (see below), we oversampled by five percent, leading to a planned sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
<!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->
In the end, `r n_finished` respondents successfully finished our study, slightly exceeding our plans.

@@

We individually checked answers for response patterns such as straight-lining or missing of inverted items.
We planned to conservatively remove participants with clear response patterns.
However, as no clear patterns emerged we maintained all participants.
We automatically excluded participants who missed the two attention checks we implemented.
Overall, 30 participants were filtered out automatically by Prolific, not counting toward our quota.
Participants who missed one attention check were checked individually regarding response patterns.
Again, no clear patterns emerged.
We planned to remove participants below the minimum participation age of 18 years.
As no minors took part in our study we did not exclude any participant for this reason.
We planned to remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
The median response time was `r round(time_med / 60, 0)` minutes and the standard deviation `r round(time_sd / 60, 0)` minutes. 
Hence, three SDs below median was `r round(time_crit_init / 60, 0)` minutes, hence not informative. 
Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
We removed `r n_speeding %>% english::english()` participants for this reason.
<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->

We planned to impute missing responses using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
However, as there were only `r n_miss(d)` answers missing in total (`r round(prop_miss(d) * 100, 3)` percent), we decided not to impute any data.
The final sample size was _N_ = `r nrow(d)`.

@@

<!-- We will test items for potential ceiling and floor effects.  -->
<!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
The factorial validity of the measures and the relations were tested using structural equation modeling. 
If Mardia’s test showed that the assumption of multivariate normality was violated, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator (or, in the few cases of missing data MLR plus FIML estimation).
We tested each scale in a confirmatory factor analysis. 
To assess model fit, we used more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
In cases of misfit, we conservatively altered models using an a priori defined analysis pipeline (see online supplementary material).
As a “reality check,” we tested items for potential ceiling and floor effects. 
If means were below 1.5 or above 6.5, we preregistered to exclude these items.
However, as no item was outside these threshold, no items were excluded.

We wanted to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we analyzed the variables' bivariate relations. 
To predict the need for privacy, we first used the six personality factors.
Afterward, we predicted privacy using the more specific facets. 
To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
However, because model fit was not acceptable we analyzed the potential effects in a multiple regression using the mean values of the observed scores. 
<!-- We will also test which individual items best predict need for privacy. -->

>>>>

abstract          : "Privacy is defined as a voluntary withdrawal from society. While everyone needs some degree of privacy, we currently know little about who needs how much. In this study, we explored the relations between the need for privacy and personality. Personality was operationalized using the HEXACO personality inventory. Need for privacy was measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy). A sample of 1,550 respondents representative of the U.S. in terms of age, gender, and ethnicity was collected. The results showed several substantial relationships: More extraverted and more agreeable people needed substantially less privacy. People less fair and less altruistic needed more psychological privacy, social privacy, and anonymity, lending some support to the 'nothing to hide-argument'. Emotionality and conscientiousness showed varied relations with need for privacy. More conservative respondents needed more privacy from the government."
keywords          : "Privacy, need for privacy, personality, HEXACO"

@@

```{r setup, include=F}
devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
library(devtools)
library(english)
library(ggplot2)
library(kableExtra)
library(lavaan)
library(magrittr)
library(naniar)
library(papaja)
library(semPlot)
library(simsem)
library(td)
library(tidyverse)

load("data/workspace_3.RData")

@@

Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2023].
Yet despite its importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155].
What can we infer about a person if they desire more privacy?
Are they more introverted, more risk-averse, or more traditional?
Asking these questions seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007], which is that people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear. 
Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
Or are people simply less extraverted, more diligent, or more prudent? 
With this paper, we seek to answer the following question: 
What can we learn about a person’s personality if they say they desire more privacy?

@@

Privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
This withdrawal happens _voluntarily_, and it is under a person's _control_ [@westinPrivacyFreedom1967]. 
Privacy is also multi-dimensional. 
On the broadest level, we can differentiate the two dimensions of horizontal and vertical privacy [@schwartzSocialPsychologyPrivacy1968; @masurPrivatheitOnlineKommunikation2018].
Whereas horizontal privacy captures withdrawal from other people or peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or businesses). 
In her theoretical analysis, @burgoonPrivacyCommunication1982 argued that privacy has four more specific dimensions: informational, social, psychological, and physical privacy. 
@pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
reserve ("unwillingness to be with and talk with others, especially strangers," p. 1293); isolation ("desire to be alone and away from others," p. 1293), solitude ("being alone by oneself and free from observation by others," p. 1293), intimacy with friends ("being alone with friends," p. 1293), intimacy with family ("being alone with members of one's own family," p. 1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention," p. 1293). 
Building on these understandings of privacy, in this study we employ a multifaceted model of need for privacy. 
We focus on _vertical_ privacy with regard to people’s felt need for withdrawal from surveillance by a) the government and b) private companies; 
_horizontal_ privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
and _general_ privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
Although all of these dimensions were defined and established in prior research, combining these dimensions into one single comprehensive measure of privacy represents a novel approach.

Acknowledging that various understandings of personality exist, we operationalize personality using the factors and facets of the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018]. 
HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant aspects than other operationalizations. 
The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
It includes six factors (discussed below), which have four specific facets each. 
In addition, the HEXACO model includes a sixth factor not present in the Big Five labeled honesty-humility, plus a meta-facet called altruism, which seem particularly well-suited to investigate the nothing-to-hide-argument.

@@

So far, only a few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
Moreover, we are not aware of a viable theory specifically connecting privacy and personality.
Due to the dearth of empirical studies and the lack of theory, in this study we hence adopt an exploratory perspective.

In order to understand how personality might relate to privacy, we can ask the following question: 
Why do people desire privacy?
Privacy is important.
But according to @trepteNeedPrivacy2017, the need for privacy is only a secondary need---not an end in itself.
Accordingly, privacy satisfies other more fundamental needs such as safety, sexuality, recovery, or contemplation.
@westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships). 
Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and thereby social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
But privacy can also have negative aspects. 
It is possible to have too much privacy.
Being cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
And privacy can also help conceal wrongdoing or crime.

Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].
Confronted with a threat---for example, the prototypical tiger---people are inclined to withdraw.
In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities. 
Indeed, the need for privacy may have evolved precisely because it offers such advantages.

@@

Empirical studies have linked privacy to increased cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
@coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
In the surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
In the privacy condition, the experimenter could not see the students. 
Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28).

We do not mean to suggest that it is only dishonest people who feel a need for privacy.
Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].
A recent study confirmed this notion, finding that people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].
Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.
Considering all the evidence, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.

@@

Emotionality is captured by the facets of fearfulness, anxiety, dependence, and sentimentality.
People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
Anxious people might hence desire more privacy. 
People who are more concerned about their privacy (in other words, more anxious about privacy) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
On the other hand, the opposite may also be true: 
People who are more anxious in general may desire less privacy from others (especially their strong ties), as a means to cope better with their daily challenges or to seek social approval to either verify or dispel their social anxiety.

@@

Comprising the facets social self-esteem, social boldness, sociability, and liveliness, extraversion is arguably the factor that should correspond most closely to need for privacy. 
Conceptually, social privacy and sociability are closely related.
More sociable people are likely more inclined to think of other people as a resource, and thus they should desire less horizontal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001]. 
Given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.

@@

Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
Arguably, all facets are about being in control, about reducing relevant risks and future costs.
Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully might prefer to have more privacy because it affords them greater control. 
Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for vertical privacy. 
In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018]. 
Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008].

@@

### Sociodemographic variables

The need for privacy should also be related to sociodemographic aspects, such as sex, age, education, and income. 
For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2023].
In a nationally representative study of the U.S. and Japan, people who were older and who had higher income reported more privacy concern. 
More educated people possess more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and as a consequence they might desire more privacy. 
Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, although not necessarily from other people. 
Some minority groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
Last, we will examine whether one’s political position is related to the need for privacy. 
We could imagine that more right-leaning people desire more privacy from the government, but not necessarily from other people.
People who are more conservative tend to trust the government slightly less [@cookSkepticalAmericanRevisiting2005], which might be associated with an increased need for privacy.
We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy.

@@

This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
The study was conducted as an online questionnaire, programmed with Qualtrics.
The survey can be found in the [online supplementary material](https://osf.io/e47yw/files/osfstorage/65c363e69b32ca0b4397f002).

@@

To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
We based our power analysis on a smallest effect size of interest (SESOI; see below).
We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. 
To estimate power, we simulated data.
We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10 (the SESOI).
We furthermore set the latent factor loadings to be $\lambda$ = .85.
Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.
A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
To account for potential attrition (see below), we over-sampled by five percent, leading to a planned sample size of _N_ = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
In the end, `r n_finished` respondents finished our study, of which we could use `r n_final`, which slightly exceeds our required sample size.

@@

We individually checked answers for response patterns such as straight-lining or missing of inverted items.
We planned to conservatively remove participants with clear response patterns.
`r patterns %>% length() %>% english %>% str_to_title()` participants were excluded because they showed clear patterns, such as straight-lining.
We automatically excluded participants who missed the two attention checks we implemented.
Overall, 30 participants were filtered out automatically by Prolific, not counting toward our quota.
Participants who missed one attention check were checked individually regarding response patterns.
No clear patterns emerged.
We planned to remove participants below the minimum participation age of 18 years.
As no minors took part in our study we did not exclude any participant for this reason.
We planned to remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
The median response time was `r round(time_med / 60, 0)` minutes and the standard deviation `r round(time_sd / 60, 0)` minutes. 
Hence, three SDs below median was `r round(time_crit_init / 60, 0)` minutes, hence not informative. 
Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
We removed `r n_speeding %>% english::english()` participants for this reason.

We planned to impute missing responses using multiple imputation with predictive mean matching (ten data-sets, five iterations, using variables that correlate at least with _r_ = .10). 
However, as there were only `r n_miss(d)` answers missing in total (`r round(prop_miss(d) * 100, 3)` percent), we decided not to impute any data.
The final sample size was _N_ = `r n_final`.

@@

The factorial validity of the measures and the relations were tested using structural equation modeling. 
If Mardia’s test showed that the assumption of multivariate normality was violated, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator (or, in the few cases of missing data MLR plus FIML estimation).
We tested each scale in a confirmatory factor analysis. 
To assess model fit, we used more liberal fit criteria to avoid over-fitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
In cases of misfit, we conservatively altered models using an a priori defined analysis pipeline (see online supplementary material).
As a “reality check,” we tested items for potential ceiling and floor effects. 
If means were below 1.5 or above 6.5, we preregistered to exclude these items.
However, as no item was outside these thresholds, no items were excluded.

We wanted to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we analyzed the variables' bivariate relations. 
To predict the need for privacy, we first used the six personality factors.
Afterward, we predicted privacy using the more specific facets. 
To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
However, because model fit was not acceptable, in exploratory analyses we investigated the potential effects in a multiple regression using the mean values of the observed scores.
